Modi normali di oscillazione del Sole (Presentazione)

### 2017-06-16 MSS.tex
cf

Sezione d'urto collisionale di Rutherford:
\begin{align*}
d\sigma=\frac{4\pi(Z_iZ_j)^2}{\mu^2(\vec{v}-\vec{v}')^4}\frac{d\chi}{\chi^3}\Label{eq:dsruther}L=\int\frac{d\chi}{\chi}=\log{(\frac{1}{\chi_{min}})}\Label{eq:cL}\lambda=\max{(r_D,a_0)}:\Label{eq:maxb}
\end{align*}

>>>>

Sezione d'urto collisionale di Rutherford:
\begin{align*}
&d\sigma=\frac{4\pi(Z_iZ_j)^2}{\mu^2(\vec{v}-\vec{v}')^4}\frac{d\chi}{\chi^3}\Label{eq:dsruther}L=\int\frac{d\chi}{\chi}=\log{(\frac{1}{\chi_{min}})}\Label{eq:cL}\\
&\lambda=\max{(r_D,a_0)}:\Label{eq:maxb}
\end{align*}
